Recent advances in random matrix theory applied to heavy-tailed multivariate time series

### 2015-08-26 papers/Number1/paper.tex
illustrated the approximation of eigenvalues.

\subsection{$\alpha \in (0,2)$: Overview of existing results: Davis et
  al., Soshnikov, Auffiner et al.}
\subsection{$\alpha \in (0,2)$: Our extension of these results; only
  order statistics of $Z_{it}$'s necessary and no sums (proof by the
  technical result)}
\subsection{$\alpha \in [2,4)$: Overview of existing results: Davis et
  al., Soshnikov, Auffiner et al.} 
\subsection{$\alpha \in [2,4)$: The problem of centering and restrictions on $p_n$}
\subsection{$\alpha \in [2,10/3)$: Our new result for the UN-CENTERED
  sample covariance matrix; only order statistics of $Z_{it}$'s
  necessary and no sums (proof by the technical result)}
\subsection{$\alpha \in [10/3,4)$: A conjecture with partial proof for
  the UN-CENTERED sample covariance matrix)}

>>>>

\subsection{$\alpha \in (0,2)$: Overview of existing results: Davis et
  al., Soshnikov, Auffiner et al.}
\subsection{$\alpha \in (0,2)$: Our extension of these results; only
  order statistics of $Z_{it}$'s necessary and no sums (proof by the
  technical result)}
To illustrate the validity of the results, we pick the following
distribution function for $Z$ and compare the eigenvalues with
the order statistics of $D_i = \sum_{t=1}^n Z_{it}^2$ and $Z^2$ using
simulated data.
\[
f(x) = {d \over dx}\P(Z \leq x) = \left\{
  \begin{array}{ll}
    {\alpha \over (4x)^{\alpha + 1}} & |x| > 1/4 \\
    \alpha & \text{ otherwise }
  \end{array}
\right.
\]
This function is shown in figure \ref{fig:densitySim}.
\begin{figure}[htb!]
  \centering
  \includegraphics[scale=0.40]{densitySim.pdf}
  \caption{Density function of simulated data. $\alpha=1.6$ is chosen
    for simulation.}
  \label{fig:densitySim}
\end{figure}
Using the simulated data, empirical density functions are obtained for
$a_{np}^{-2}\lambda_{(i)} - a_{np}^{-2}D_{(i)}$ and
$a_{np}^{-2}\lambda_{(i)} - a_{np}^{-2}Z^2_{(i)}$. These are shown in
figure \ref{fig:lambda_comparison}.
\begin{figure}[htb!]
  \centering
  \includegraphics[scale=0.40]{lambda_comparison.pdf}
  \caption{A total of 20000 pairs are compared in each case.}
  \label{fig:lambda_comparison}
\end{figure}

\subsection{$\alpha \in [2,4)$: Overview of existing results: Davis et
  al., Soshnikov, Auffiner et al.} 
\subsection{$\alpha \in [2,4)$: The problem of centering and restrictions on $p_n$}
\subsection{$\alpha \in [2,10/3)$: Our new result for the UN-CENTERED
  sample covariance matrix; only order statistics of $Z_{it}$'s
  necessary and no sums (proof by the technical result)}
\subsection{$\alpha \in [10/3,4)$: A conjecture with partial proof for
  the UN-CENTERED sample covariance matrix)}
